Source Summaries

### 2020-04-06 paper/sourceSummaries/summary7.tex
added joshua's 7th source summary

@@

@@

@@

@@

@@

@@

@@

\noindent
\subsection{Portable RFID Bumping Device}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{dijkPortableBumping}

@@

\noindent
The authors proposed that RFID cards may be vulnerable to a high speed cloning attack performed by bumping into the target.  They posit that this attach can be used to gain clones of security cards without the target's knowledge or raising suspicion.

@@

\noindent
Game Theory.  By showing the ease of cloning the cards the authors show that they are broken and need increased security in order to stay useful.

@@

\noindent
The authors used a Proxmark 3, a LG Nexus 5 with Nethunter, a Hirose usb cable, MIFARE Classic 1K, and MIFARE Classic EV1 1K.  The authors wrote a default key to the cards and then a large number of random keys.  They then generated a large number of random keys to try and gathered a large number of nonces to perform their attack.

@@

\noindent
The authors found that the HF Hirose Antenna increased the range to 6-8cm.  They also successfully implemented BTWA to read multiple cards.  The attacks against the cards were successefully performed against both the Classic and the Classic EV1.

@@

\noindent
The authors posit that more research can be done into the maximum number of cards that can be read at one time.  They also believes that the attack framework can be extended to support more attacks, optimization can be performed on the keyspace calculation software, attempts can be made to try the attack in an unstable environment, and finally optimazation of the Proxmark firmware.

>>>>

\noindent
\subsection{{O}n {B}ad {R}andomness and {C}loning of {C}ontactless {P}ayment and {B}uilding {S}mart {C}ards}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{6565237}

@@

\noindent
The authors describe the problems with the Mifare Classic RFID card's random number generator and examine the real life implications of bad key generation.

@@

\noindent
Game Theory.  The authors explore the possibility of directly attacking MiFare cards, through the Random Number Generator and otherwise.

@@

\noindent
The authors review recent revelations about MiFare random number generation and describe the problem with entropy.  They then review the probability distribution of the random number generators for Mifare cards.

@@

\noindent
The authors found that random number generators in small cards like the Mifare are often not secure.  They found that using problems in random number generators allow for very easily breaking security in many smart cards.

@@

\noindent
The authors do not describe any formal future directions, but one obvious future direction would be doing research on more vendors of smart cards.

@@

@@

@@

@@

@@

@@

@@
